\title{Tower Defence Game}
\author{Aidan Saull}
\date{\today}

\documentclass[12pt]{article}

\begin{document}
\maketitle

\section*{Basics}

\begin{itemize}
\item Players play as government contractors tasked with saving the Earth
\item Same starting contract amount
\item After the first wave, the defense budget is split according to exactly how
much work each company did
\item In subsequent rounds, the defense budget is spent relative to how much
each contractor contributed relative to their budget. (if all contractors do 
poorly relative to their contracts, they can all secure more money later)
\item The player who had the worst performance will lose money due to damages
if any enemies get through to the Earth.
\item Game ends once the Earth is destroyed or all waves are cleared (maybe,
waves may be infinite)
\item Winner is the player with the biggest overall profit.
\end{itemize}

\section*{Gameplay}
\begin{itemize}
\item Enemies have health and shields, some weapons work better on health and
some on shields
\item We do the math on how much it ``costs'' to destroy a point of shield vs
a point of health and adjust performance scores accordingly
\item First round enemies have only health and no shield
\item Later enemies will tend to continue on a health and shield percent trend,
however sometimes a round will counter the trend.
\item Turrets are placed in any circular orbit. Orbits below 400km will decay
after three rounds no matter what, all other orbits will never decay.
\item Cost to put a turret into orbit increase as the orbit height increases.
This is rewarded due to the fact that late game turrets have large ranges much
greater than say 400km. Putting a 2000km range turret 600km above the earth is
inefficient as range is wasted. Additionally, some of the best high range
turrets cannot shoot through the Earth, and they will therefore see more if
they are higher. Thirdly, high orbit turrets can achieve higher performance
(idk what I meant by this). Fourthly, some enemies will move slowly at a high
orbit, but very quickly through lower orbits.
\item Turrets orbit at appropriate speeds. This means that turrets may,
through bad luck have a very poor performance in any given round.
\end{itemize}

\section*{Economy - based on obsevations}
\begin{itemize}
\item \textbf{\textit{At no point in the development of this game will I ever
attempt to allow spending no money to be a legitimate strategy.}}
\item This section will be filled as observations about the economy round to
round are made.
\end{itemize}


\section*{Phases}
The game will be divided into two main phases, Purchasing and Defending.
\subsection*{Purchasing}
During this phase the game will be paused, and all satellites will be at their ``default''
positions. The player will be able to:
\begin{itemize}
\item Purchase satellites
\item Repair satellites
\item Adjust the orbit of satellites that are capable of orbit adjustment
\end{itemize}
\subsection*{Defending}
During this phase, time will become unpaused and the satellites will begin their orbits
around the planet. The player will not be able to do anything except for watch.

\section*{Classes}

\subsection*{GameController}
\subsubsection*{Private Attributes}
\begin{itemize}
\item \texttt{player\_list} - list of \texttt{Corporation}
\item \texttt{base\_health}
\item \texttt{round\_number}
\item \texttt{enemy\_shield\_percent} - apprx. percent of enemies health that is
shield.
\item \texttt{enemy\_shield\_pierce\_percent} - apprx. percent of enemies that
fire shield piercing weapons
\item \texttt{enemy\_types} - list of \texttt{Enemy}
\item \texttt{game\_state} - what stage the game is on. \texttt{Build},\
\texttt{Combat}, or \texttt{Recap}
\item \texttt{defence\_budget}
\end{itemize}
\subsubsection*{Public Attributes}
\begin{itemize}
\item 
\end{itemize}
\subsubsection*{Methods/Functions}
\begin{itemize}
\item \texttt{calculate\_budgets} - returns the a list of budgets for each
of the corporations
\item \texttt{start\_game}
\item \texttt{start\_round} - begins spawning of enemies and activates defences
\item \texttt{end\_round} - sums up the round, awards contracts and adjusts
global budget
\end{itemize}



\subsection*{Corporation}
\subsubsection*{Private Attributes}
\begin{itemize}
\item \texttt{budget}
\item \texttt{funds}
\item \texttt{performance} - Score of enemies destroyed
\end{itemize}
\subsubsection*{Public Attributes}
\begin{itemize}
\item 
\end{itemize}
\subsubsection*{Methods/Functions}
\begin{itemize}
\item \texttt{get\_budget} - returns last round's budget
\item \texttt{set\_budget(budget)} - sets the budget for next round
\item \texttt{get\_performance(performance)} - returns last round's performance
\item \texttt{update} - will monitor for player input when placing defences
\item \texttt{place\_defence(defence\_type, position)}
\end{itemize}


\subsection*{Defence} A generic defense. Only children of this class will ever
be instantiated.
\subsubsection*{Private Attributes}
\begin{itemize}
\item \texttt{health}
\item \texttt{shield}
\item \texttt{altitude}
\item \texttt{current\_target} - an \texttt{Enemy} that this turret is currently
targeting
\item \texttt{upgrades} - a dictionary with keys as upgrade types, and values as
upgrade descriptions
\item \texttt{current\_upgrades} - a dictionary with keys as upgrade types, and
values as the current level of that upgrade.
\end{itemize}
\subsubsection*{Public Attributes}
\begin{itemize}
\item 
\end{itemize}
\subsubsection*{Methods/Functions}
\begin{itemize}
\item \texttt{update} - set enemy to target, call attack, call move - 
\textit{Not Implemented}
\item \texttt{attack(enemy)} - attack designated enemy
\item \texttt{upgrade(upgrade\_type)} - upgrade this defence by the specified
type once, returns True if completed, or False if not possible.
\item \texttt{move} - simply orbit the Earth.
\end{itemize}

\subsection*{Enemy} A generic enemy. Only children of this class will ever
be instantiated.
\subsubsection*{Private Attributes}
\begin{itemize}
\item \texttt{health}
\item \texttt{shield}
\item \texttt{current\_target} - a \texttt{defence} that this turret is
currently targeting
\end{itemize}
\subsubsection*{Public Attributes}
\begin{itemize}
\item 
\end{itemize}
\subsubsection*{Methods/Functions}
\begin{itemize}
\item \texttt{update} - set defence to target, call attack, call move - 
\textit{Not Implemented}
\item \texttt{attack(enemy)} - attack designated defence
\item \texttt{move} - choose a path to follow down to the surface
\end{itemize}




\end{document}
  
